\textls[-0]{\thetitle}

### 2023-03-24 metatheory-condensed.tex
edit

In rules \ruleref{l/add} and \ruleref{lsig/add},
the third premise $\goodTerm{\Gm,x : \TyTkg{\lsig}}{\seal}{A}$ is
responsible for hiding W-type signatures.
Here, $\TyTkg{\lsig}$ packages $\lsig$---recall that $\lsig$ contains the
(self-parameterized) types of all the fields preceding the current
field~$t$---into a dependent tuple type (\ruleref{tyeq/pk/add}).
The term $\seal$ turns a tuple of type $\TyTkg{\lsig}$ into a new tuple of type~$A$
that hides W-type signatures behind $\cU$, if necessary.\footnote{%
In the presence of hiding, it is important that the context type~$A$ be a
dependent tuple type rather than a linkage type; we expand on this point in an
appendix.}
%
It is straightforward to find the~$\seal$ that fits the bill, though this process
is not automated in \TT.
In particular, when no hiding is needed, $\seal$ is simply~$x$,
%\EDJ{$\var{0}$ is not identity (substitution), but the first variable, right? Or you meant to say it is identity ``sealing''?}\YZreply{Yes, I meant identity sealing. I cannot say 'sealing' because the paper currently does not use the word sealing anywhere.}\EDJreply{What about just remove the parenthesis and ``the identity''}
and $A$ is $\TyTkg{\lsig}$.
In \cref{fig:stlc-linkage-typing}, $\seal_1$, $\seal_2$, and $\seal_{10}$ are simply $x$,
while $\seal_6$ hides $"tm" : \TyS{\wcode{\wsig_{\texttt{tm}}}}$
as $"tm" : \cU$ in $A_6$
so that the typing of~$t_6$ is oblivious to the concrete signature
$\wsig_{\texttt{tm}}$ and therefore can be reused.
%\begingroup
%\fontsize{9}{9}\selectfont%
%\goodTerm{
%  x :
%  \big[\texttt{tm} : \TyS{\wcode{\wsig_{\texttt{tm}}}},\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
%}{
%  \seal_6
%}{
%  \big[\texttt{tm} : \cU,\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
%}.
%\endgroup

>>>>

In rules \ruleref{l/add} and \ruleref{lsig/add},
the third premise $\goodTerm{\Gm,x : \TyTkg{\lsig}}{\seal}{A}$ is
responsible for hiding W-type signatures.
Here, $\TyTkg{\lsig}$ packages $\lsig$---recall that $\lsig$ contains the
(self-parameterized) types of all the fields preceding the current
field~$t$---into a dependent tuple type (\ruleref{tyeq/pk/add}).
The term $\seal$ turns a tuple of type $\TyTkg{\lsig}$ into a new tuple of type~$A$
that hides W-type signatures behind $\cU$, if necessary.\footnote{%
In the presence of hiding, it is important that the context type~$A$ be a
dependent tuple type rather than a linkage type; we expand on this point in an
appendix.}

It is straightforward to find the~$\seal$ that fits the bill, though this process
is not automated in \TT.
In particular, when no hiding is needed (that is, when the field being checked
invokes a W-type constructor or eliminator), $\seal$ is simply~$x$,
and $A$ is $\TyTkg{\lsig}$.
In \cref{fig:stlc-linkage-typing}, $\seal_2$ and $\seal_{10}$ are~$x$.
%\EDJ{$\var{0}$ is not identity (substitution), but the first variable, right? Or you meant to say it is identity ``sealing''?}\YZreply{Yes, I meant identity sealing. I cannot say 'sealing' because the paper currently does not use the word sealing anywhere.}\EDJreply{What about just remove the parenthesis and ``the identity''}
Otherwise, it is needed to hide W-type signatures. In \cref{fig:stlc-linkage-typing},
$\seal_6$ hides $"tm" : \TyS{\wcode{\wsig_{\texttt{tm}}}}$
as $"tm" : \cU$ in~$A_6$,
so that~$t_6$, typed under $\mathit{self}:A_6$, is oblivious to the concrete signature
$\wsig_{\texttt{tm}}$ and therefore can be reused.
%\begingroup
%\fontsize{9}{9}\selectfont%
%\goodTerm{
%  x :
%  \big[\texttt{tm} : \TyS{\wcode{\wsig_{\texttt{tm}}}},\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
%}{
%  \seal_6
%}{
%  \big[\texttt{tm} : \cU,\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
%}.
%\endgroup
